## Quantstrat II

```{r 002a-comment-1, eval = FALSE}
# http://www.r-programming.org/papers
```

```{r 002a-symbols}
symbols <- basic_symbols()
```

```{r 002a-getSymbols}
getSymbols(Symbols = symbols,
           src = "yahoo",
           index.class = "POSIXct",
           from = start_date,
           to = end_date,
           adjust = adjustment)
```

```{r 002a-stock}
stock(symbols, currency = "USD", multiplier = 1)
```

### multiAsset.bb1

```{r 002a-strat-vars}
SD <- 2
N <- 20
```

```{r 002a-init}
strategy.st <- "bbands"
portfolio.st <- "multiAsset.bb1"
account.st <- "multiAsset.bb1"
```

```{r 002a-rm-strat}
rm.strat(portfolio.st)
rm.strat(account.st)
```

```{r 002a-init-portf}
initPortf(name = portfolio.st,
          symbols = symbols,
          initDate = init_date)
```

```{r 002a-init-acct}
initAcct(name = account.st,
         portfolios = portfolio.st,
         initDate = init_date,
         initEq = init_equity)
```

```{r 002a-init-orders}
initOrders(portfolio = portfolio.st,
           symbols = symbols,
           initDate = init_date)
```

```{r 002a-strategy}
strategy(strategy.st, store = TRUE)
```

```{r 002a-add-indicators}
add.indicator(strategy.st, 
              name = "BBands",
              arguments = list(HLC = quote(HLC(mktdata)), 
                               maType = "SMA"), 
              label = "BBands")
```

```{r 002a-add-signals}
add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("Close", "up"), 
                            relationship = "gt"), 
           label = "Cl.gt.UpperBand")

add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("Close", "dn"), 
                            relationship = "lt"), 
           label = "Cl.lt.LowerBand")

add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("High", "Low", "mavg"), 
                            relationship = "op"), 
           label = "Cross.Mid")
```

```{r 002a-add-rules}
add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "Cl.gt.UpperBand", 
                          sigval = TRUE, 
                          orderqty = -100, 
                          ordertype = "market", 
                          orderside = NULL), 
         type = "enter")

add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "Cl.lt.LowerBand", 
                          sigval = TRUE, 
                          orderqty = 100, 
                          ordertype = "market", 
                          orderside = NULL), 
         type = "enter")

add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "Cross.Mid", sigval = TRUE, 
                          orderqty = "all", 
                          ordertype = "market", 
                          orderside = NULL), 
         type = "exit")
```

```{r 002a-apply-strategy, results = "hide"}
out <- applyStrategy(strategy.st,
                    portfolios = portfolio.st,
                    parameters = list(sd = SD, n = N))
```

```{r 002a-update}
updatePortf(portfolio.st)
updateAcct(account.st)
updateEndEq(account.st)
```

```{r 002a-checkBlotterUpdate}
checkBlotterUpdate(portfolio.st, account.st, verbose = TRUE)
```

```{r 002a-chart-posn}
for(symbol in symbols) {
    chart.Posn(portfolio.st, Symbol = symbol,
               TA = "add_BBands(n = 20, sd = 2)")
}
```

### multiAsset.bb2

```{r 002b-init}
strategy.st <- "bbands"
portfolio.st <- "multiAsset.bb2"
account.st <- "multiAsset.bb2"
```

```{r 002b-rm-strat}
rm.strat(portfolio.st)
```

```{r 002b-init-portf}
initPortf(name = portfolio.st, 
          symbols, 
          initDate = init_date)
```

```{r 002b-init-account}
initAcct(name = account.st, 
         portfolios = portfolio.st,
         initDate = init_date, 
         initEq = init_equity)
```

```{r 002b-init-orders}
initOrders(portfolio = portfolio.st, 
           initDate = init_date)
```

```{r 002b-strat-vars}
SD <- 3
```

```{r 002b-apply-strategy}
out <- applyStrategy(strategy.st,
                     portfolios = portfolio.st,
                     parameters = list(sd = SD, n = N))
```

```{r 002b-update}
updatePortf(portfolio.st)
updateAcct(account.st)
updateEndEq(account.st)
```

```{r 002b-checkBlotterUpdate}
checkBlotterUpdate(portfolio.st, account.st, verbose = TRUE)
```

```{r 002b-chart-posn}
for(symbol in symbols) {
    chart.Posn(portfolio.st, Symbol = symbol,
               TA = "add_BBands(n = 20, sd = 2)")
}
```

### Compare Strategies

```{r}
eq1 <- getAccount("multiAsset.bb1")$summary$End.Eq
rt1 <- Return.calculate(eq1, "log")
eq2 <- getAccount("multiAsset.bb2")$summary$End.Eq
rt2 <- Return.calculate(eq2, "log")
returns <- cbind(rt1, rt2)
colnames(returns) <- c("SD = 2","SD = 3")
chart.CumReturns(returns, colorset = c(2, 4), legend.loc = "topleft", 
                 main = "BBand SD Parameter Comparison", ylab = "cum return", 
                 xlab = "", minor.ticks = FALSE)
```

### Order Sizing

#### osFixedDollar()

This order sizing function adjusts the share quantity such that the transaction value is approximately equal to a pre-defined tradesize

$$ \text{orderqty } = \frac{\text{tradeSize}}{\text{ClosePrice}} $$

```{r}
osFixedDollar <- function(timestamp, orderqty, portfolio, symbol, ruletype, ...) {
    ClosePrice <- as.numeric(Cl(mktdata[timestamp,]))
    orderqty <- round(tradeSize/ClosePrice, -2)
    return(orderqty)
}
```

### Fixed-Dollar Order Sizing

#### Strategy Variables

```{r 002c-strategy-vars}
fastMA <- 12
slowMA <- 26
signalMA <- 9
maType = "EMA"
tradeSize <- init_equity/10
```

```{r 002c-init}
strategy.st <- "macd"
portfolio.st <- "multi.macd"
account.st <- "multi.macd"
```

```{r 002c-rm-strat}
rm.strat(portfolio.st)
```

```{r 002c-init-portf}
initPortf(name = portfolio.st, 
          symbols, 
          initDate = init_date)
```

```{r 002c-init-account}
initAcct(name = account.st, 
         portfolios = portfolio.st,
         initDate = init_date, 
         initEq = init_equity)
```

```{r 002c-init-orders}
initOrders(portfolio = portfolio.st, 
           initDate = init_date)
```

```{r 002c-strategy}
strategy(strategy.st, store = TRUE)
```

#### Add Indicators

```{r 002c-add-indicators}
add.indicator(strategy.st, 
              name = "MACD", 
              arguments = list(x = quote(Cl(mktdata))), 
              label = "osc")
```

#### Add Signals

```{r 002c-add-signals}
add.signal(strategy.st, 
           name = "sigThreshold", 
           arguments = list(column = "signal.osc", 
                            relationship = "gt", 
                            threshold = 0, 
                            cross = TRUE), 
           label = "signal.gt.zero")

add.signal(strategy.st, 
           name = "sigThreshold", 
           arguments = list(column = "signal.osc", 
                            relationship = "lt", 
                            threshold = 0, 
                            cross = TRUE), 
           label = "signal.lt.zero")
```

#### Add Rules

```{r 002c-add-rules}
add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "signal.gt.zero", 
                          sigval = TRUE, 
                          orderqty = 100, 
                          ordertype = "market", 
                          orderside = "long", 
                          osFUN = "osFixedDollar"), 
         type = "enter", 
         label = "enter", 
         storefun = FALSE)

add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "signal.lt.zero", 
                          sigval = TRUE, 
                          orderqty = "all", 
                          ordertype = "market", 
                          orderside = "long"), 
         type = "exit", 
         label = "exit")
```

#### Apply Strategy

```{r}
out <- applyStrategy(strategy.st, 
                     portfolios = portfolio.st, 
                     parameters = list(nFast = fastMA, nSlow = slowMA, 
                                       nSig = signalMA, maType = maType), 
                     verbose = TRUE)
```

```{r 002c-update}
updatePortf(portfolio.st)
updateAcct(account.st)
updateEndEq(account.st)
```

```{r 002c-checkBlotterUpdate}
checkBlotterUpdate(portfolio.st, account.st, verbose = TRUE)
```

#### Chart Positions

```{r 002c-chart-posn}
for(symbol in symbols) {
    chart.Posn(Portfolio = portfolio.st, 
               Symbol = symbol)
    add_MACD()
    add_EMA(12, col = "red")
    add_EMA(26, col = "blue")
}
```

### Max Position Order Sizing

```{r 002d-strategy-vars}
strategy.st <- "bb.lim"
SD <- 2
N <- 20
```

```{r 002d-strategy}
strategy(strategy.st, store = TRUE)
```

```{r 002d-add-indicators}
add.indicator(strategy.st, 
          name = "BBands", 
          arguments = list(HLC = quote(HLC(mktdata)), 
                           maType = "SMA"), 
          label = "BBands")
```

```{r 002d-add-signals}
add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("Close", "up"), 
                            relationship = "gt"), 
           label = "Cl.gt.UpperBand")

add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("Close", "dn"), 
                            relationship = "lt"), 
           label = "Cl.lt.LowerBand")

add.signal(strategy.st, 
           name = "sigCrossover", 
           arguments = list(columns = c("High", "Low", "mavg"), 
                            relationship = "op"), 
           label = "Cross.Mid")
```

```{r 002d-add-rules}
add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "Cl.gt.UpperBand", 
                          sigval = TRUE, 
                          orderqty = -1000, 
                          ordertype = "market", 
               orderside = NULL, 
               osFUN = "osMaxPos"), 
         type = "enter")

add.rule(strategy.st, name = "ruleSignal", 

         arguments = list(sigcol = "Cl.lt.LowerBand", 
                          sigval = TRUE, 
                          orderqty =  1000, 
                          ordertype = "market", 
               orderside = NULL, 
               osFUN = "osMaxPos"), 
         type = "enter")

add.rule(strategy.st, 
         name = "ruleSignal", 
         arguments = list(sigcol = "Cross.Mid", 
                          sigval = TRUE, 
                          orderqty =  "all", 
                        ordertype = "market",
                        orderside = NULL), 
         type = "exit")
```

#### Position Limits

```{r 002d-remove-portf}
rm.strat("multi.bb.limit") # remove portfolio, account, orderbook if re-run
```

```{r 002d-init-objects}
initPortf(name = "multi.bb.limit", 
          symbols, 
          initDate = init_date)
initAcct(name = "multi.bb.limit", 
         portfolios = "multi.bb.limit",
initDate = init_date, 
initEq = init_equity)
initOrders(portfolio = "multi.bb.limit", 
           initDate = init_date)
```

#### addPosLimit()

```{r 002d-addPosLimit}
for(symbol in symbols) {
    addPosLimit("multi.bb.limit", 
                symbol = symbol, 
                timestamp = init_date, 
                maxpos = 200, 
                longlevels = 2 )
}
```

#### Apply Strategy

```{r 002d-apply-strategy}
out <- applyStrategy(strategy.st, 
                     portfolios = "multi.bb.limit", 
                     parameters = list(sd = SD, n = N))
```

```{r 002d-update}
updatePortf("multi.bb.limit")
updateAcct("multi.bb.limit")
updateEndEq("multi.bb.limit")
```

```{r 002d-checkBlotterUpdate}
checkBlotterUpdate("multi.bb.limit", "multi.bb.limit")
```

