# Connor's RSI(2)

Let's step our analysis up a notch. First, we're going to run an analysis on twelve symbols. We're also going to add some conditional signals. 

The strategy we're going to use will be similar to Connor's RSI(2). The rules we'll apply are:

1. BTO if Cl > SMA(200) and RSI(2) < 5

1. sTC if Cl < SMA(200) or Cl > SMA(5)

```{r, message = FALSE, warnings = FALSE}
library(quantstrat)
library(TTR)
```

```{r}
Sys.setenv(TZ = "UTC")
```

```{r}
symbols <- c("IWM", "SPY", "QQQ", "XLF", "XLP", "XLE",
             "XLY", "XLV", "XLI", "XLB", "XLK", "XLU")
```

```{r}
currency("USD")
```

## Get Symbols

```{r}
init_date <- "2009-12-31"

start_date <- "2010-01-01"

end_date <- "2010-12-31"

init_equity <- 1e4 # $10,000
```

```{r}
getSymbols(Symbols = symbols, 
           src = "yahoo", 
           index.class = "POSIXct",
           from = start_date, 
           to = end_date, 
           adjust = TRUE)
```

```{r}
stock(symbols, currency = "USD", multiplier = 1)
```

## Initialize Account, Portfolio and Strategy

```{r}
strat.name <- "Connors.RSI.2"
```

```{r}
rm.strat(strat.name)
```

```{r}
initPortf(strat.name, 
          symbols = symbols, 
          initDate = init_date)
```

```{r}
initAcct(strat.name, 
         portfolios = strat.name, 
         initDate = init_date, 
         initEq = init_equity)
```

```{r}
initOrders(portfolio = strat.name, 
           symbols = symbols, 
           initDate = init_date)
```

```{r}
strategy(strat.name, store = TRUE)
```

```{r}
strat <- getStrategy(strat.name)
```

## Indicators

For our strategy, we need to add three indicators: SMA(5), SMA(200) and RSI(2). All of our indicators will use a simple moving average based on closing prices. 

```{r 2-1-add-indicators}
add.indicator(strategy = strat.name, 
              name = "RSI", 
              arguments = list(price = quote(getPrice(mktdata)), 
                               n = 2, 
                               maType = "SMA"), 
              label = "RSI2")

add.indicator(strategy = strat.name, 
              name = "SMA", 
              arguments = list(x = quote(Cl(mktdata)), 
                               n = 5), 
              label = "SMA5")

add.indicator(strategy = strat.name, 
              name = "SMA", 
              arguments = list(x = quote(Cl(mktdata)), 
                               n = 200), 
              label = "SMA200")
```

## Signals

```{r 2-1-add-signals}
add.signal(strat.name, 
           name="sigThreshold", 
           arguments = list(threshold = 5, 
                            column = "RSI2", 
                            relationship = "lt", 
                            cross = FALSE),
           label = "RSI2.lt.5")

add.signal(strat.name, 
           name="sigCrossover", 
           arguments = list(columns = c("Close", "SMA5"), 
                            relationship = "gte"),
           label="Cl.gte.SMA5")

add.signal(strat.name,
           name = "sigComparison",
           arguments = list(columns = c("Close", "SMA200"),
                            relationship = "lt"),
           label = "Cl.lt.SMA200")

add.signal(strat.name, 
           name = "sigFormula", 
           arguments = list(columns = c("RSI2.lt.5", "Cl.lt.SMA200"), 
                            formula = "RSI2.lt.5 == TRUE & 
                                        Cl.lt.SMA200 == FALSE", 
                            label = "trigger", 
                            cross = TRUE), 
           label = "Buy")

```

## Adding Rules

```{r 2-1-add-rules}
add.rule(strat.name, 
         name = 'ruleSignal',
         arguments = list(sigcol = "Buy", 
                          sigval = TRUE, 
                          orderqty = 100,
                          ordertype = 'market', 
                          orderside = 'long'),
         type = 'enter')

add.rule(strat.name,
         name = 'ruleSignal',
         arguments = list(sigcol = "Cl.lt.SMA200",
                          sigval = TRUE,
                          orderqty = 'all',
                          ordertype = 'market',
                          orderside = 'long'),
         type = 'exit')

add.rule(strat.name, 
         name = 'ruleSignal',
         arguments = list(sigcol = "Cl.gte.SMA5", 
                          sigval = TRUE, 
                          orderqty = 'all',
                          ordertype = 'market', 
                          orderside = 'long'),
         type = 'exit')
```

```{r, results = "hide"}
# Trade output suppressed for length
applyStrategy(strategy = strat.name, 
              portfolios = strat.name)
```

## Update Portfolio, Account

```{r 2-1-update-portfolio}
updatePortf(strat.name)
updateAcct(strat.name)
updateEndEq(strat.name)
```

### Per Trade Stats

```{r 2-1-trade-stats, include = TRUE}
knitr::kable(t(tradeStats(strat.name))[-c(1:2), 1:6], 
             caption = "Trade Stats per Symbol")

knitr::kable(t(tradeStats(strat.name))[-c(1:2), 7:12], 
             caption = "Trade Stats per Symbol")
```

## Returns

```{r}
for(symbol in symbols) {
    chart.Posn(Portfolio = strat.name, 
               Symbol = symbol, 
               TA = c("add_RSI(n = 2, maType = 'SMA')", 
                      "add_SMA(n = 5, col = 4, on = 1, lwd = 2)", 
                      "add_SMA(n = 200, col = 2, on = 1, lwd = 2)"))
}
```

## Equity Curve

```{r}
a <- getAccount(strat.name)
equity <- a$summary$End.Eq
plot(equity, main = "Consolidated Equity Curve")
```

