# Get Symbols

We start off by loading `basic_symbols()` into the `symbols` variable:

```{r get-symbols-symbols}
print(basic_symbols())

symbols <- basic_symbols()
```

`getSymbols()` is part of the `quantmod` package which was automatically loaded when we loaded `quantstrat`. It should have been installed automatically when you install `quantstrat`. 

We send a request through `getSymbols()` to download data. We can use any of the following sources:

* Yahoo!

* Google

* MySQL

* RData

* CSV

For data other than stocks we can use:

* [FRED (Federal Reserve Economic Data) source](https://research.stlouisfed.org/fred2/);  FRED contains data such as unemployment, GDP, treasury rates and more. 

* [OANDA](https://www.oanda.com/) is a subscription-service for forex and currency data. 

## Yahoo!

```{r get-symbols-yahoo-getsymbols}
getSymbols(Symbols = symbols, 
           src = "yahoo", 
           index.class = "POSIXct",
           from = start_date, 
           to = end_date, 
           adjust = adjustment)
```

The first thing you notice is the warning message. As it states, it will only appear the first time you run `getSymbols()` in a new session.

```{r get-symbols-comment-1, include = FALSE}
#' What is this message stating exactly and how will the next version of 
#'      quantmod affect our code?
```

* **Symbols**: one or a vector of multiple symbols. 

* **src**: string, our source. In this case, Yahoo!

* **index.class**: POSIXct. This sets the class of our xts object index. 

* **from**: string, first date of data we want to retrieve

* **end**: string, last date of data we want to retrieve

* **adjust**: boolean, whether to adjust our data or not. Suggested to set as TRUE.

`getSymbols` will load xts objects for each of the symbols we passed into our Global Environment. We can view the data as we would any other dataset.

```{r get-symbols-remove-yahoo-symbols}
head(IWM)
tail(IWM)
summary(IWM)
# Clear symbols
rm(list=basic_symbols())
```

## Google

```{r get-symbols-google-getsymbols}
getSymbols(Symbols = symbols, 
           src = "google", 
           index.class = "POSIXct",
           from = start_date, 
           to = end_date, 
           adjust = adjustment)
```

We access data from Google same as Yahoo! only changing the **src** parameter. 

```{r get-symbols-remove-google-symbols}
head(IWM)
tail(IWM)
summary(IWM)
# Clear symbols
rm(list=basic_symbols())
```

## MySQL

```{r get-symbols-hidden-1, include = FALSE}
source("../.my.conf.R")
```

```{r get-symbols-mysql-getsymbols}
getSymbols(Symbols = symbols, 
           src = "MySQL", 
           dbname = db, 
           user = user, 
           password = pw, 
           host = host,
           index.class = "POSIXct",
           from = start_date, 
           to = end_date, 
           adjust = adjustment)
```

To load data via MySQL database we need to supply additional parameters: **dbname**, **user**, **password** and **host**. **user** needs to have SELECT privileges but nothing more for our purposes.

`getSymbols()` does not currently permit passing database values via a my.cnf file. The parameters are checked early in the function so either you need to include them in the call or include them in a hidden R file outside of your project directory and source the file.

Your database should contain a table named by symbol, one for each symbol. Each table should have the following fields: **date**, **o**, **h**, **l**, **c**, **v** and **a**. If your table has different field names you must add them to the *db.fields* parameter as a character vector. 

You can also change the names of the fields as they are imported into R by using the *field.names* parameter. However, none of that is required as long as *db.fields* meets the default criteria. 

The data in my database is a duplicate of Yahoo!. The output below is to show the success of the `getSymbols(src="MySQL")` call.

```{r get-symbols-remove-mysql-symbols}
head(IWM)
tail(IWM)
summary(IWM)
# Clear symbols
rm(list=basic_symbols())
```

## FRED

For this example we'll bail on the `symbols` we have been using prior. FRED contains over 11,000 econonomic datasets at no cost. 

Let's look at the 10-Year Treasury Rate:

> https://research.stlouisfed.org/fred2/series/DGS10

Notice the tail of the url has the alphanumeric string **DGS10** which we will be using in our `getSymbols()` call. 

```{r get-symbols-fred-getsymbols}
getSymbols(Symbols = "DGS10", src = "FRED")
```

Notice our call is shorter than previous; we do not need to classify index nor do we need to adjust any data. 

In addition, passing data parameters doesn't seem to do anything; the entire dataset is returned. 

I'll use `quantmod::chartSeries()` to plot the data:

```{r get-symbols-dgs10-chartseries}
chartSeries(DGS10)
```

```{r get-symbols-remove-DGS10}
rm(DGS10)
```

## OANDA

Contributions needed.
