# Stop Loss Optimization {#stop-loss-optimization}

We take the code from \@ref(stop-loss) and reuse it here this time to test parameters for our stop-loss just as we did in \@ref(parameter-optimization). This time though instead of optimizing indicators we're going to optimize `.stopLoss` in a new integer vector `.StopLoss`. 

```{r stop-loss-optimization-strategy-vars}
.StopLoss = seq(0.05, 0.6, length.out = 48)/100
```

We'll name this strategy `Luxor.Stop.Loss.Opt`. 

```{r stop-loss-optimization-strategy}
strategy.st <- "Luxor.Stop.Loss.Opt"

rm.strat(portfolio.st)
rm.strat(account.st)

initPortf(name = portfolio.st,
          symbols = symbols,
          initDate = init_date)

initAcct(name = account.st,
         portfolios = portfolio.st,
         initDate = init_date)

initOrders(portfolio = portfolio.st,
           initDate = init_date)

strategy(strategy.st, store = TRUE)
```

## Add Indicators

```{r stop-loss-optimization-add-indicators}
add.indicator(strategy.st, 
              name = "SMA",
              arguments = list(x = quote(Cl(mktdata)),
                               n = .fast),
              label = "nFast")

add.indicator(strategy.st, 
              name = "SMA",
              arguments = list(x = quote(Cl(mktdata)),
                               n = .slow),
              label = "nSlow")
```

## Add Signals

```{r stop-loss-optimization-add-signals}
add.signal(strategy.st, 
           name = "sigCrossover",
           arguments = list(columns = c("nFast", "nSlow"),
                            relationship = "gte"),
           label = "long"
)
add.signal(strategy.st, 
           name = "sigCrossover",
           arguments = list(columns = c("nFast", "nSlow"),
                            relationship = "lt"),
           label = "short")
```

## Add Rules

```{r stop-loss-optimization-add-rules}
add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "long" , 
                          sigval = TRUE,
                          replace = FALSE,
                          orderside = "long" ,
                          ordertype = "stoplimit",
                          prefer = "High",
                          threshold = .threshold,
                          TxnFees = .txnfees,
                          orderqty = +.orderqty,
                          osFUN = osMaxPos,
                          orderset = "ocolong"),
         type = "enter",
         label = "EnterLONG")

add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "short", 
                          sigval = TRUE,
                          replace = FALSE,
                          orderside = "short",
                          ordertype = "stoplimit",
                          prefer = "Low",
                          threshold = .threshold,
                          TxnFees = .txnfees,
                          orderqty = -.orderqty,
                          osFUN = osMaxPos,
                          orderset = "ocoshort"),
         type = "enter",
         label = "EnterSHORT")

add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "short", 
                          sigval = TRUE,
                          replace = TRUE,
                          orderside = "long" ,
                          ordertype = "market",
                          TxnFees = .txnfees,
                          orderqty = "all",
                          orderset = "ocolong"),
         type = "exit",
         label = "Exit2SHORT")

add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "long", 
                          sigval = TRUE,
                          replace = TRUE,
                          orderside = "short",
                          ordertype = "market",
                          TxnFees = .txnfees,
                          orderqty = "all",
                          orderset = "ocoshort"),
         type = "exit",
         label = "Exit2LONG")

add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "long" , 
                          sigval = TRUE,
                          replace = FALSE,
                          orderside = "long",
                          ordertype = "stoplimit",
                          tmult = TRUE,
                          threshold = quote(.stoploss),
                          TxnFees = .txnfees,
                          orderqty = "all",
                          orderset = "ocolong"),
         type = "chain", 
         parent = "EnterLONG",
         label = "StopLossLONG",
         enabled = FALSE)

add.rule(strategy.st, 
         name = "ruleSignal",
         arguments = list(sigcol = "short", 
                          sigval = TRUE,
                          replace = FALSE,
                          orderside = "short",
                          ordertype = "stoplimit",
                          tmult = TRUE,
                          threshold = quote(.stoploss),
                          TxnFees = .txnfees,
                          orderqty = "all",
                          orderset = "ocoshort"),
         type = "chain", 
         parent = "EnterSHORT",
         label = "StopLossSHORT",
         enabled = FALSE)
```

## Add Position Limit

```{r stop-loss-optimization-add-pos-limit}
for(symbol in symbols){
    addPosLimit(portfolio = portfolio.st,
                symbol = symbol,
                timestamp = init_date,
                maxpos = .orderqty)
}
```

## Add Distribution

We use `add.distribution` again to assign our `.StopLoss` vector as values for the **StopLossLONG** and **StopLossSHORT** rule chains. 

```{r stop-loss-optimization-add-distribution}
add.distribution(strategy.st,
                 paramset.label = "StopLoss",
                 component.type = "chain",
                 component.label = "StopLossLONG",
                 variable = list(threshold = .StopLoss),
                 label = "StopLossLONG")

add.distribution(strategy.st,
                 paramset.label = "StopLoss",
                 component.type = "chain",
                 component.label = "StopLossSHORT",
                 variable = list(threshold = .StopLoss),
                 label = "StopLossSHORT")
```

## Add Distribution Constraint

We set a distribution constraint to keep the **StopLossLONG** and **StopLossSHORT** parameters the same. 

```{r stop-loss-optimization-add-distribution-constraint}
add.distribution.constraint(strategy.st,
                            paramset.label = "StopLoss",
                            distribution.label.1 = "StopLossLONG",
                            distribution.label.2 = "StopLossSHORT",
                            operator = "==",
                            label = "StopLoss")
```

## Enable Rules

```{r stop-loss-optimization-enable-rules}
enable.rule(strategy.st, 'chain', 'StopLoss')
```

## Apply Paramset

```{r stop-loss-optimization-apply-paramset, results = "hide"}
cwd <- getwd()
setwd("./_data/")
results_file <- paste("results", strategy.st, "RData", sep = ".")
if( file.exists(results_file) ) {
    load(results_file)
} else {
    results <- apply.paramset(strategy.st, 
                              paramset.label = "StopLoss", 
                              portfolio.st = portfolio.st, 
                              account.st = account.st, 
                              nsamples = .nsamples, 
                              verbose = TRUE)
    
    if(checkBlotterUpdate(portfolio.st, account.st, verbose = TRUE)) {
        save(list = "results", file = results_file)
        save.strategy(strategy.st)
    }
}
setwd(cwd)
```
